---
title: "Descriptive Statistics "
author: "Venkata babu Aalapati"
date: "11/19/2022"
output: word_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(utf8)
library(ggplot2)
library(aod)
library(outliers)
library(readxl)
library(Hmisc)
```

```{r}
dplyr::summarize 
#loading the data set  

df_good_belly <- read_excel("Goodbelly_Project_Data.xlsx")
#removing null values from the data set
na.omit(df_good_belly)
#viewing the columns of the data set
head(df_good_belly)
#Creating new dataframe with all numeric columns
df_good_belly_numeric = df_good_belly[,c(4:12)]
```

```{r}
#statitical summary of the numerical columns in the goddbelly data set
summary(df_good_belly_numeric)
```

```{r}
#Extract the values of the potential outliers based on the IQR criterion 
 ggplot(df_good_belly) +
  aes(x = "", y = ARP) +
  geom_boxplot(fill = "#0c4c8a") +
  theme_minimal()
boxplot.stats(df_good_belly$ARP)$out

```

```{r}
#Extract the values of the potential outliers based on the IQR criterion 
ggplot(df_good_belly) +
  aes(x = "", y = Sales) +
  geom_boxplot(fill = "#0c4c2a") +
  theme_minimal()
boxplot.stats(df_good_belly$Sales)$out
```
Grubbs’s test:
With box plots we observed some data points with high and low values in the data set, for futher analysis we conducted the grubs statitical test
The Grubbs test allows to detect whether the highest or lowest value in a dataset is an outlier.
The Grubbs test detects one outlier at a time (highest or lowest value),
so the null and alternative hypotheses are as follows:
H0: The highest value is not an outlier
H1: The highest value is an outlier
if we want to test the highest value, or: 
H0: The lowest value is not an outlier
H1: The lowest value is an outlier if we want to test the lowest value.

As for any statistical test, if the p-value is less than the chosen significance threshold (generally alpha = 0.10 ) then the null hypothesis is rejected and we will conclude that the lowest/highest value is an outlier. On the contrary, if the p-value is greater or equal than the significance level, the null hypothesis is not rejected, and we will conclude that, based on the data, we do not reject the hypothesis that the lowest/highest value is not an outlier.

```{r}
test_high_arp <- grubbs.test(df_good_belly_numeric$ARP)
test_high_arp
test_low_arp<-grubbs.test(df_good_belly_numeric$ARP, opposite = TRUE)
test_low_arp
```

```{r}
test_high_sales <- grubbs.test(df_good_belly_numeric$Sales)
test_high_sales
test_low_sales<-grubbs.test(df_good_belly_numeric$Sales, opposite = TRUE)
test_low_sales
```




```{r}
#histogram density plot to understand sales 
library(Hmisc)

X<-df_good_belly$Sales
hist(X,
main="Distribution of Sales",
xlab="Sales",
xlim=c(0,1050),
col="darkmagenta",
freq=FALSE
)
#histogram frequency  plot to understand sales 
hist.data.frame(df_good_belly['Sales'])
#histogram density plot to understand ARP


X<-df_good_belly$ARP
hist(X,
main="Distribution of ARP",
xlab="Sales",
xlim=c(2.5,6.5),
col="darkorange",
freq=FALSE
)
#histogram frequency  plot to understand ARP
hist.data.frame(df_good_belly['ARP'])
```

```{r}

```

