---
title: "Model3"
author: "Venkata babu Aalapati"
date: "11/22/2022"
output: word_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(utf8)
library(ggplot2)
library(aod)
library(outliers)
library(readxl)
library(Hmisc)
```

```{r}
#loading the data set
df_good_belly <- read_excel("Goodbelly_Project_Data.xlsx")
#removing null values from the data set
na.omit(df_good_belly)
```

Model3:
(Model2C + Region:Endcap Interaction) 
Sales = β0 + β1Region + β2Demo + β3Demo1.3 + β4Demo4.5 + β5Endcap
+ β6Region ∗ Endcap + β7Sales_Rep 
```{r}
#Building basic regression model
Model3<-lm(formula = Sales ~ Region+Demo+Demo1.3+Demo4.5+Endcap
             +Region*Endcap+Sales_Rep ,
            data = df_good_belly)

#Understanding summary results of the model
summary(Model3)

# Plotting fitted residuals  model
plot(Model3, which=1, col=c("blue"))

# Plotting residuals and find the variation left by unexplained by the model
df_good_belly$predicted <- predict(Model3)   # Save the predicted values
df_good_belly$residuals <- residuals(Model3) # Save the residual values
ggplot(df_good_belly, aes(x = Region, y = Sales)) +
  geom_smooth(method = "lm", se = FALSE, color = "lightgrey") +    
  geom_segment(aes(xend = Region, yend = predicted), alpha = .2) +      
  geom_point(aes(color = abs(residuals), size = abs(residuals))) +  
  scale_color_continuous(low = "green", high = "red") +             
  guides(color = FALSE, size = FALSE) +                             
  geom_point(aes(y = predicted), shape = 1) +
  theme_bw()
```

```{r}
#Generating CI intervals for coefficients with alpha 0.10
confint(Model3,level = 0.90)
confint.default(Model3)
#Doing wald test for further analysis on coefficients
wald.test(b = coef(Model3), Sigma = vcov(Model3), Terms = 1:26)
#Generating CI intervals for odds ratio of coeeficents with alpha 0.10
exp(coef(Model3))
exp(cbind(OR = coef(Model3), confint(Model3,level = 0.90)))
```

```{r}
#Further analysis with on residuals with diagnostic plots 
opar <- par(mfrow = c(2,2), oma = c(0, 0, 1.1, 0)) 
plot(Model3, las = 1)
```

Model3A:
(Model3 + Store + Store:Endcap Interaction) 
Sales = β0 + β1Region + β2Endcap + β3Demo + β4Demo1.3 + β5Demo4.5 
+ β6Region ∗ Endcap + β7Store + β8Store ∗ Endcap + βSales_Rep
```{r}
#Building basic regression model
Model3A<-lm(formula = Sales ~ Region+Endcap+Demo+Demo1.3+Demo4.5
             +Region*Endcap+Sales_Rep+Store+Store*Endcap+Sales_Rep ,
            data = df_good_belly)
#Understanding summary results of the model
summary(Model3A)

# Plotting fitted residuals  model
plot(Model3A, which=1, col=c("blue"))

# Plotting residuals and find the variation left by unexplained by the model
df_good_belly$predicted <- predict(Model3A)   # Save the predicted values
df_good_belly$residuals <- residuals(Model3A) # Save the residual values
ggplot(df_good_belly, aes(x = Store, y = Sales)) +
  geom_smooth(method = "lm", se = FALSE, color = "lightgrey") +    
  geom_segment(aes(xend = Store, yend = predicted), alpha = .2) +      
  geom_point(aes(color = abs(residuals), size = abs(residuals))) +  
  scale_color_continuous(low = "green", high = "red") +             
  guides(color = FALSE, size = FALSE) +                             
  geom_point(aes(y = predicted), shape = 1) +
  theme_bw()
```

```{r}
#Generating CI intervals for coefficients with alpha 0.10
confint(Model3A,level = 0.90)
confint.default(Model3A)
#Doing wald test for further analysis on coefficients
#wald.test(b = coef(Model3A), Sigma = vcov(Model3A),Terms = 1:5)
#Generating CI intervals for odds ratio of coefficients with alpha 0.10
exp(coef(Model3A))
exp(cbind(OR = coef(Model3A), confint(Model3A,level = 0.90)))
```

```{r}
#Further analysis with on residuals with diagnostic plots 
opar <- par(mfrow = c(2,2), oma = c(0, 0, 1.1, 0)) 
plot(Model3A, las = 1)
```

Model3B:
(Model3 + Region:Demo Interaction) 
Sales = β0 + β1Region + β2Endcap + β3Demo + β4Demo1.3 + β5Demo4.5
+ β6Region ∗ Endcap + β8Region ∗ Demo + β7Sales_Rep 
```{r}
#Building basic regression model
Model3B<-lm(formula = Sales ~ Region+Endcap+Demo+Demo1.3+Demo4.5
             +Region*Endcap+Region*Demo+Sales_Rep ,
            data = df_good_belly)
#Understanding summary results of the model
summary(Model3B)


# Plotting fitted residuals  model
plot(Model3B, which=1, col=c("blue"))

# Plotting residuals and find the variation left by unexplained by the model
df_good_belly$predicted <- predict(Model3B)   # Save the predicted values
df_good_belly$residuals <- residuals(Model3B) # Save the residual values
ggplot(df_good_belly, aes(x = Region, y = Sales)) +
  geom_smooth(method = "lm", se = FALSE, color = "lightgrey") +    
  geom_segment(aes(xend = Region, yend = predicted), alpha = .2) +      
  geom_point(aes(color = abs(residuals), size = abs(residuals))) +  
  scale_color_continuous(low = "green", high = "red") +             
  guides(color = FALSE, size = FALSE) +                             
  geom_point(aes(y = predicted), shape = 1) +
  theme_bw()
```

```{r}
#Generating CI intervals for coefficients with alpha 0.10
confint(Model3B,level = 0.90)
confint.default(Model3B)
#Doing wald test for further analysis on coefficients
wald.test(b = coef(Model3B), Sigma = vcov(Model3B), Terms = 1:10)
#Generating CI intervals for odds ratio of coefficients with alpha 0.10
exp(coef(Model3B))
exp(cbind(OR = coef(Model3B), confint(Model3B,level = 0.90)))
```

```{r}
#Further analysis with on residuals with diagnostic plots 
opar <- par(mfrow = c(2,2), oma = c(0, 0, 1.1, 0)) 
plot(Model3B, las = 1)
```

Model3C:
(Model3+: Demo/Demo Interactions)
Sales = β0 + β1Region + β2Endcap + β3Demo + β4Demo1.3 + β5Demo4.5 
+β6Region∗Endcap+β7Demo∗Demo1.3+Demo1.3∗Demo4.5+Demo∗Demo4.5+β7Sales_Rep 

```{r}
#Building basic regression model

Model3C<-lm(formula = Sales ~ Region+Endcap+Demo+Demo1.3+Demo4.5
             +Region*Endcap+Demo*Demo1.3*Demo4.5+Demo*Demo4.5+Sales_Rep ,
            data = df_good_belly)
#Understanding summary results of the model
summary(Model3C)

# Plotting fitted residuals  model
plot(Model3C, which=1, col=c("blue"))

# Plotting residuals and find the variation left by unexplained by the model
df_good_belly$predicted <- predict(Model3C)   # Save the predicted values
df_good_belly$residuals <- residuals(Model3C) # Save the residual values
ggplot(df_good_belly, aes(x = Demo, y = Sales)) +
  geom_smooth(method = "lm", se = FALSE, color = "lightgrey") +    
  geom_segment(aes(xend = Demo, yend = predicted), alpha = .2) +      
  geom_point(aes(color = abs(residuals), size = abs(residuals))) +  
  scale_color_continuous(low = "green", high = "red") +             
  guides(color = FALSE, size = FALSE) +                             
  geom_point(aes(y = predicted), shape = 1) +
  theme_bw()
```

```{r}
#Generating CI intervals for coefficients with alpha 0.10
confint(Model3C,level = 0.90)
confint.default(Model3C)
#Doing wald test for further analysis on coefficients
#wald.test(b = coef(Model3C), Sigma = vcov(Model3C), Terms = 1:30)
#Generating CI intervals for odds ratio of coeeficents with alpha 0.10
exp(coef(Model3C))
exp(cbind(OR = coef(Model3C), confint(Model3C,level = 0.90)))
```

```{r}
#Further analysis with on residuals with diagnostic plots 
opar <- par(mfrow = c(2,2), oma = c(0, 0, 1.1, 0)) 
plot(Model3C, las = 1)
```


Model3D:
(Model3+ Demo:Demo1.3 Interaction) 
Sales = β0 + β1Region + β2Endcap + β3Demo + β4Demo1.3 + β5Demo4.5
+ β6Region ∗ Endcap + β7Demo ∗ Demo1.3 + β7Sales_Rep 

```{r}
#Building basic regression model
Model3D<-lm(formula = Sales ~ Region+Endcap+Demo+Demo1.3+Demo4.5
             +Region*Endcap+Demo*Demo1.3+Sales_Rep ,
            data = df_good_belly)
#Understanding summary results of the model
summary(Model3D)

# Plotting fitted residuals  model
plot(Model3D, which=1, col=c("blue"))

# Plotting residuals and find the variation left by unexplained by the model
df_good_belly$predicted <- predict(Model3D)   # Save the predicted values
df_good_belly$residuals <- residuals(Model3D) # Save the residual values
ggplot(df_good_belly, aes(x = Demo, y = Sales)) +
  geom_smooth(method = "lm", se = FALSE, color = "lightgrey") +    
  geom_segment(aes(xend = Demo, yend = predicted), alpha = .2) +      
  geom_point(aes(color = abs(residuals), size = abs(residuals))) +  
  scale_color_continuous(low = "green", high = "red") +             
  guides(color = FALSE, size = FALSE) +                             
  geom_point(aes(y = predicted), shape = 1) +
  theme_bw()
```

```{r}
#Generating CI intervals for coefficients with alpha 0.10
confint(Model3D,level = 0.90)
confint.default(Model3D)
#Doing wald test for further analysis on coefficients
wald.test(b = coef(Model3D), Sigma = vcov(Model3D), Terms = 1:10)
#Generating CI intervals for odds ratio of coeeficents with alpha 0.10
exp(coef(Model3D))
exp(cbind(OR = coef(Model3D), confint(Model3D,level = 0.90)))
```

```{r}
#Further analysis with on residuals with diagnostic plots 
opar <- par(mfrow = c(2,2), oma = c(0, 0, 1.1, 0)) 
plot(Model3D, las = 1)
```